Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-03-18 manuscript.qmd
sample different simple models

```{python}
#| echo: false
#| label: fig-burnin-history
#| layout-ncol: 2
#| fig-cap: Monitoring quantities during the burn-in phase of the parameter sampling.
#| fig-subcap: 
#|   - "Autocorrelation time"
#|   - "log likelihood"

import pandas as pd
import matplotlib.pyplot as plt
from tueplots import figsizes, fontsizes

plt.rcParams.update(figsizes.icml2024_half())
plt.rcParams.update(fontsizes.icml2024())

burnin_history = pd.read_csv("models/midline_history.csv").set_index("steps")

plt.plot(
  burnin_history.index,
  burnin_history.acor_times,
)
plt.show()

plt.plot(
  burnin_history.index,
  burnin_history.max_log_probs,
)
plt.show()
```

>>>>

```{python}
#| echo: false
#| label: fig-burnin-history
#| layout-ncol: 1
#| layout-nrow: 1
#| fig-cap: Monitoring quantities during the burn-in phase of the parameter sampling.
#| fig-subcap: 
#|   - "Autocorrelation time"
#|   - "log likelihood"
from collections import namedtuple

import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
from tueplots import figsizes, fontsizes

nrows, ncols = 1, 3
label_map = {
  "acor_times": "Autocorrelation [steps]",
  "accept_fracs": "Sample Acceptance [%]",
  "max_log_probs": "Maximum log-Likelihood",
}

plt.rcParams.update(figsizes.icml2024_full(nrows=nrows, ncols=ncols))
plt.rcParams.update(fontsizes.icml2024())

fig, axes = plt.subplots(
  nrows=nrows,
  ncols=ncols,
  sharex=True,
)

for model in ["ipsi", "contra", "bilateral", "midline"]:
  history = pd.read_csv(f"models/{model}/history.csv").set_index("steps")
  for i, column in enumerate(history.columns):
    history.plot(y=column, ax=axes[i], label=model)
    axes[i].autoscale(enable=True, tight=True, axis="x")
    axes[i].set_title(label_map[column])

plt.show()
```
